---
title: "Assigment - kNN DIY"
author:
  - Veronika Cintulova - Author
  - Sandra Tadić - Reviewer
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---

```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
```

------------------------------------------------------------------------

Choose a suitable dataset from [this](https://github.com/HAN-M3DM-Data-Mining/assignments/tree/master/datasets) folder and train your own kNN model. Follow all the steps from the CRISP-DM model.

## Business Understanding

Occupancy detection data set This dataset is a set of data such as: Temperature, Light, Humidity and Co2 measurements.These data are being obtained every minute. It is supposed to predict whether the room is occupied or not.This can be very useful when having a big building with a lot of meeting/conference rooms, without having an employee taking care of evidence of occupancy of the rooms. Instead of spending money for an employee, or a camera systems that can disturb the privacy of people in the rooms, this model can predict whether the room is empty or not.

## Data Understanding

```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-occupancy.csv"
rawDF <- read_csv(url)
```
```{r}
str(rawDF)
```

The dataset has 7 variables (columns) and 8,146 observations (rows)

## Data Preparation

```{r}
cleanDF <- rawDF[-1]
head(cleanDF)
```

We would like to predict the occupancy of the rooms.

```{r}
cntOcc <- table(cleanDF$Occupancy)
propOcc <- round(prop.table(cntOcc) * 100 , digits = 1)

cntOcc
```

```{r}
propOcc
```

```{r}
cleanDF$Occupancy <- factor(cleanDF$Occupancy, levels = c("0", "1"), labels = c("Non_occupied", "Occupied")) %>% relevel("Occupied")
head(cleanDF, 10)
```

```{r}
summary(cleanDF[c("Temperature", "Humidity", "Light", "CO2")])
```

```{r}
normalize <- function(x) { 
  return ((x - min(x)) / (max(x) - min(x))) 
}

testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10

cat("testSet1:", testSet1, "\n")

cat("testSet2:", testSet2, "\n")

cat("Normalized testSet1:", normalize(testSet1), "\n")

cat("Normalized testSet2:", normalize(testSet2))
```

```{r}
nCols <- dim(cleanDF)[2]
cleanDF_n <- sapply(2:nCols,
                    function(x) {
  normalize(rawDF[,x])
}) %>% as.data.frame()

summary(cleanDF_n[c("Temperature", "Humidity", "Light", "CO2")])
```

```{r}
trainDF_feat <- cleanDF_n[1:469,  ]
testDF_feat <- cleanDF_n[470:569,  ]
```

```{r}
trainDF_labels <- cleanDF[1:469,  6]
testDF_labels <- cleanDF[470:569,  6]
```

## Modeling

```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 21)
head(cleanDF_test_pred)
```

## Evaluation and Deployment

```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```

Prediction is that the room will not be occupied, on the other hand, the positive class from this data-set is: occupied. Either we can see some disadvantages of the KNN model and some model is better to use in this example, or the code could have been done better. I would appreciate the reviewer's or teacher's adivise/suggestions.

reviewer adds suggestions for improving the model
